### 2019-10-14 paper/abstract.tex
Last edits in abstract.tex
Just a few minor grammar mistakes.

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. Additionally, the neutron spectrum shift during the reactor operation was calculated. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel. Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

>>>>

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. Additionally, the neutron spectrum shift during the reactor operation was calculated. The results showed that the continuous flow of Pu reactor-grade helps transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel. Finally, using \gls{TRU} as initial fissile materials proved the possibility of operating the SD-TMSR for a extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}
